---
title: "`r params$title`"
author: "`r params$author`"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
params:
  title: "Example Hospital Flow Report"
  author: "CLAHRC NWL Information Intelligence Team"
  hospital_name: "Anytown General Hospital"
  import_list_path: "../example-config/example_import_list.rds"
  sample_weeks: 1
  sample_no_of_patients: 100
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(magrittr)

sample_duration <- lubridate::duration(params$sample_weeks, "weeks")
sample_no_of_patients <- params$sample_no_of_patients
```

Package version: `r stringr::str_sub(system("git rev-parse HEAD", intern=TRUE), 1, 8)`

Number of weeks used as sample: `r params$sample_weeks`

Number of patients sampled: `r params$sample_no_of_patients`

```{r import-data, cache=TRUE, echo=FALSE}
# Import and Standardise Data

import_list <- readRDS(params$import_list_path)

# This import list uses relative paths (good for us during development)
# which means the paths need prepending with "../" to work from the
# working directory used in running this file.
# In production use, users will be best specifying their import paths
# as absolute paths.
import_list <- lapply(import_list, function(x) {
  list(data_path = paste0("../", x$data_path),
  config_path = paste0("../", x$config_path),
  site = x$site,
  facility = x$facility,
  time_zone = x$time_zone)
})

data_list <- hospitalflow::import_standardise_bind(import_list)
```

```{r spell-table, cache=TRUE, echo=FALSE}
ed_data <- data_list[["ED"]]
inpatient_data <- data_list[["IP"]]

data_start_date <- as.Date(max(min(ed_data$start_datetime, na.rm = TRUE),
                       min(ed_data$end_datetime, na.rm = TRUE),
                       min(inpatient_data$start_datetime, na.rm = TRUE),
                       min(inpatient_data$end_datetime, na.rm = TRUE)))
data_end_date <- as.Date(min(max(ed_data$start_datetime, na.rm = TRUE),
                     max(ed_data$end_datetime, na.rm = TRUE),
                     max(inpatient_data$start_datetime, na.rm = TRUE),
                     max(inpatient_data$end_datetime, na.rm = TRUE)))
start_date <- data_start_date
end_date <- data_end_date

#samples down by time frame
if(!is.na(sample_duration)) {
  
  data_start_date <- lubridate::ceiling_date(data_start_date, "month")
  data_end_date <- lubridate::floor_date(data_end_date, "month")
  
  if(data_end_date - data_start_date > sample_duration) {
    start_date <- data_end_date - sample_duration
    end_date <- data_end_date
    example_ed_data <- ed_data %>% dplyr::filter(start_datetime <= end_date,
                                                 end_datetime >= start_date)
    example_inpatient_data <- inpatient_data %>% dplyr::filter(start_datetime <= end_date,
                                                               end_datetime >= start_date)
  } else {
    example_ed_data <- ed_data
    example_inpatient_data <- inpatient_data
  }
} else {
  example_ed_data <- ed_data
  example_inpatient_data <- inpatient_data
}

#samples down by number of patients 
if(!is.na(sample_no_of_patients)) {
  
  inpatients <- levels(factor(example_inpatient_data$pseudo_id))
  sample_inpatients <- sample(inpatients, sample_no_of_patients)
  
  example_ed_data <- example_ed_data %>% 
    dplyr::filter(pseudo_id %in% sample_inpatients)
  
  example_inpatient_data <- example_inpatient_data %>%
    dplyr::filter(pseudo_id %in% sample_inpatients)

} 

example_spell_table <- hospitalflow::make_spell_table(ed_data = example_ed_data,
                                                      inpatient_data = example_inpatient_data)

example_spell_table <- hospitalflow::add_spell_variables(ed_data = example_ed_data,
                                                         inpatient_data = example_inpatient_data,
                                                         spell_table = example_spell_table)
```
## Dataset
This report is based on `r nrow(example_ed_data)` emergency department attendances and `r nrow(example_inpatient_data)` inpatient episodes of care, linked into `r nrow(example_spell_table)` hospital spells. All attendances and admissions occurred prior to `r end_date` and all discharges after `r start_date`.

## Age and Gender

```{r age-gender-ed, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
hospitalflow::ae_attendances_admissions_age_sex(start_date = start_date, end_date = end_date,
                                                data = example_spell_table,
                                                plot_chart = TRUE,
                                                hospital_name = params$hospital_name)
```

## Arrival Occupancy

```{r arr-occ, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
hospitalflow::ae_arrival_occupancy(start_date = as.POSIXct(start_date, tz = "Europe/London"),
                                   end_date = as.POSIXct(end_date, tz = "Europe/London"),
                                   data = example_spell_table,
                                   plot_chart = TRUE,
                                   hospital_name = params$hospital_name)
```

## Four hour performance by flow group

```{r four-hour-flow-group, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
# hospitalflow::four_hrs_perf_flow_groups(start_dt = as.Date(start_date),
#                                    end_dt = as.Date(end_date),
#                                    data = example_spell_table,
#                                    time_unit = "day",
#                                    plot_chart = TRUE,
#                                    hospital_name = "Anytown General Hospital")
```

## Duration in ED by flow group

```{r crisis-spike, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE }
hospitalflow::ed_los_flow_grps(start_date = start_date, end_date = end_date,
                             data = example_spell_table,
                             plot_chart = TRUE,
                             hospital_name = params$hospital_name)
```



## Duration in ED by admitted/non-admitted

```{r los-ed, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
hospitalflow::los_att_adm_ae(start_date = start_date, end_date = end_date,
                             data = example_spell_table,
                             plot_chart = TRUE,
                             hospital_name = params$hospital_name)
```

## Duration in ED by flow group

```{r los-ed-flow,  echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
# hospitalflow::average_ed_los_flows(start_date = start_date, end_date = end_date,
#                              data = example_spell_table,
#                              plot_chart = TRUE,
#                              hospital_name = params$hospital_name)
```



## Admissions and Discharges by Day of Week


```{r adm-disch-dow, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
hospitalflow::admissions_discharges(start_date = start_date, end_date = end_date,
                                    data = example_spell_table,
                                    plot_chart = TRUE,
                                    hospital_name = params$hospital_name)
```


## Length of Stay

```{r los-dist, echo=F, results='asis', fig.height=5, fig.width=7, cache=TRUE}
hospitalflow::los_distrib_method_admission(start_date = start_date, end_date = end_date,
                                           data = example_spell_table,
                                           plot_chart = TRUE,
                                           hospital_name = params$hospital_name)
```

## Alternative ED occupancy by hour of week
```{r ed-occ-1, echo=F, results='asis', fig.height=5, fig.width=7, fig.align = 'left', cache=TRUE}
hospitalflow::occupancy_weekday_hour(start_date = as.POSIXct(start_date, tz = "Europe/London"),
                                   end_date = as.POSIXct(end_date, tz = "Europe/London"),
                                   data = example_spell_table,
                                   plot_chart = TRUE,
                                   hospital_name = params$hospital_name)
```

## Monthly 7-day Readmission Rate
```{r readm-7, echo=F, results='asis', fig.height=5, fig.width=7, fig.align = 'left', cache=TRUE}
hospitalflow::readmissions_ip(start_date = as.POSIXct(start_date, tz = "Europe/London"),
                              end_date = as.POSIXct(end_date, tz = "Europe/London"),
                              data = example_spell_table,
                              plot_chart = TRUE,
                              hospital_name = params$hospital_name,
                              readmission_by = 7)
```

## Monthly 30-day Readmission Rate
```{r readm-30, echo=F, results='asis', fig.height=5, fig.width=7, fig.align = 'left', cache=TRUE}
hospitalflow::readmissions_ip(start_date = as.POSIXct(start_date, tz = "Europe/London"),
                              end_date = as.POSIXct(end_date, tz = "Europe/London"),
                              data = example_spell_table,
                              plot_chart = TRUE,
                              hospital_name = params$hospital_name,
                              readmission_by = 30)
```

## Monthly 90-day Readmission Rate
```{r readm-90, echo=F, results='asis', fig.height=5, fig.width=7, fig.align = 'left', cache=TRUE}
hospitalflow::readmissions_ip(start_date = as.POSIXct(start_date, tz = "Europe/London"),
                              end_date = as.POSIXct(end_date, tz = "Europe/London"),
                              data = example_spell_table,
                              plot_chart = TRUE,
                              hospital_name = params$hospital_name,
                              readmission_by = 90)
```
